Active Learning : From Blackbox To Timed Connectors

### 2016-01-06 paper/paper.tex
.

\subsection{Reo Coordination Language}
\label{sec:reo}

@@

\subsection{Time Axis}
Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.\todo{citations}
Generally, these models are designed to handle real-time behavior where time is defined in
$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
easier\todo{citations}.

\subsection{Parameterized Mealy Machine}
We present a model named \emph{parameterized mealy machine} to represent timed connectors. This
model is supposed to behave as a middle representation. Connectors are defined as parameterized
mealy machines, and composed via its production operator. Then original mealy-machine model will be
taken as semantics of PMM model.

\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
  alphabet to its corresponding Mealy Machine. 
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereafter referred to as an alphabet)
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I$ is a finite set of source-ends.
    \item[-] $O$ is a finite set of sink-ends.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow Output(\Sigma, O)$ to denote the output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

@@

>>>>

\subsection{Reo Coordination Language}
\label{sec:reo}
Reo Coordination Language\cite{DBLP:journals/mscs/Arbab04}

@@

\subsection{Time Domain}
Time is involved in several extension of Reo like timed Reo, hybrid Reo, etc.
Generally, these models are designed to handle real-time behavior where time is defined in
$\mathbb{R}$. However, we also found a lot of works where authors use rational time to make things
easier\todo{citations}.

In this paper, we choose the rational number field $\mathbb{Q}$ as our time domain, which simplifies
discretization of timed behaviors greatly.

As presented in section \ref{sec:reo}, all real-time behavior in timed Reo comes with the
\emph{t-timer} channels, and the number of these channels are apparently finite. We use
$t_i\in\mathbb{Q}$ to denote the delays of these timer channels, and now we can define a precision
function $prec$.
\[
prec(t_1,\cdots,t_n) = \max_T\{\forall t_i.\exists n_i\in\mathbb{N}.t_i=n_i\cdot T\}
\]
It's easy to prove that such a $T$ is always existing.

In real systems, the concept \emph{time precision} is widely used with the name ``clock-period''.
Most of the time, we know the clock-cycle of some hardware components, even without any idea of its
structure. With such precision $T$ given, it's reasonable to assume that all $t$-timers are actually
$nT$-timers. In following sections, we'll use $n$-timers instead.

Besides, we're going to add a single ``T'' action in mealy machines. It indicates that a transition
will take a time unit to finish, and all outputs would come out after that.

\subsection{Parameterized Mealy Machine}
We present a model named \emph{parameterized mealy machine} to represent timed connectors
(hereinafter referred to as PMM). This
model is supposed to behave as a middle representation. Connectors are defined as parameterized
mealy machines, and composed via its production operator. Then original mealy-machine model will be
taken as semantics of PMM model.

\begin{definition}[Parameterized Mealy Machine]
  A \emph{Parameterized Mealy Machine} is defined as a function $\mathcal{PM}(\Sigma)=\langle
  S(\Sigma), s_0, I, O, \delta(\Sigma), \lambda(\Sigma)\rangle$ that maps an
  alphabet to its corresponding Mealy Machine. 
  \begin{itemize}
    \item[-] $\Sigma$ is a \emph{finite} datum alphabet (hereinafter referred to as an alphabet)
    \item[-] $S$ is a function that maps an alphabet to a \emph{finite} set of
      states. We use $S(\Sigma)$ to denote the state set.
    \item[-] $I$ is a finite set of source-ends.
    \item[-] $O$ is a finite set of sink-ends.
    \item[-] $s_0$ is the initial state. It satisfies $\forall \Sigma,s_0\in S(\Sigma)$
    \item[-] $\delta$ maps a \emph{finite} datum alphabet to an \emph{output function}. We use
      $\delta(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow Output(\Sigma, O)$ to denote the output function.
    \item[-] $\lambda$ maps an alphabet to a \emph{transition function}. We use
      $\lambda(\Sigma):S(\Sigma)\times Input(\Sigma,I)\rightarrow S(\Sigma)$ to denote the transiton
      function.
  \end{itemize}
\end{definition}

@@

\todo{example of production, maybe fifo+timer}
